---
title: "Tags"
page-layout: article
format:
  html:
    css: list.css
    toc: true
    toc-location: left
    toc_depth: 2
---

<script src="copyText.js"></script>

```{r, echo=FALSE}
source("functions.R")
```

To add tags to your r-exams markdown file add ```exextra[]:` to the ```Meta-information` of your markdown file.

We have four categories that can be applied.

## Click to search

<ol class="bullet">
<li><strong>Type</strong>:
`r copyOnClick("Calculation")`
`r copyOnClick("Case")`
`r copyOnClick("Conceptual")`
`r copyOnClick("Creating graphs")`
`r copyOnClick("Data manipulation")`
`r copyOnClick("Interpreting graph")`
`r copyOnClick("Interpreting output")`
`r copyOnClick("Performing analysis")`
`r copyOnClick("Test choice")`
</li>
<li><strong>Program</strong>:
`r copyOnClick("SPSS")`
`r copyOnClick("JASP")`
`r copyOnClick("R")`
`r copyOnClick("STATA")`
`r copyOnClick("Excel")`
`r copyOnClick("Calculator")`
`r copyOnClick("Jamovi")`
</li>
<li><strong>Language</strong>:
`r copyOnClick("English")`
`r copyOnClick("Dutch")`
</li>
<li><strong>Level</strong>:
`r copyOnClick("Statistical Literacy")`
`r copyOnClick("Statistical Reasoning")`
`r copyOnClick("Statistical Thinking")`
</li>
</ol>

You can use more than one tag per category.

```{}
Meta-information
================
exextra[Type]: Calculation, Data manipulation
exextra[Program]: SPSS
exextra[Language]: English
exextra[Level]: Statistical Literacy
```

## Type descriptions

```{r, echo=FALSE, warning=FALSE, message=FALSE, , results='asis', comment=NA}
library(readxl)
library(kableExtra)
  type <- read_excel("source/Taxonomie ShareStats versie 17 maart 2021.xlsx", sheet = 2)

# datatable(type[1:9,-2], rownames = FALSE)

  # kbl(type[1:9,-2]) %>%
  # kable_material(c("striped", "hover")) %>%
  # kable_styling(full_width = F) %>%
  # column_spec(1, bold = T, border_right = T) %>%
  # column_spec(2, width = "30em") %>%
  # column_spec(3, width = "30em")

for(row in 1:9) {

  html.results <- cat(paste0("<h5><strong>",type[row,1],"</strong></h5><p>",type[row,3],"</p><p><strong>Example:</strong>: ", type[row,4],"</p>") )

}
```

### Level descriptions

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(readxl)
level <- read_excel("source/Taxonomie ShareStats versie 17 maart 2021.xlsx", sheet = 3)

# datatable(type[1:9,-2], rownames = FALSE)
```

<h5>`r level[1,1]`</h5>

<p>`r level[1,2]`</p>

<p><strong>Example</strong>: `r level[1,3]`</p>

<h5>`r level[2,1]`</h5>

<p>`r level[2,2]`</p>

<p><strong>Example</strong>: `r level[2,3]`</p>

<h5>`r level[3,1]`</h5>

<p>`r level[3,2]`</p>

<p><strong>Example</strong>: `r level[3,3]`</p>

## ShareStats project

More information on the ShareStats project can be found on [our website](http://www.sharestats.nl).
