---
title: "Statistics Taxonomy"
page-layout: article
output:
  html_document:
    css: list.css
    toc: true
    toc_float: true
    toc_depth: 2
---

Below you can find the statistics taxonomy used in ShareStats. You can click on each taxonomy level te get a sub selection of only those items in the itembank.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(readxl)
library(data.tree)
library(htmltools)
library(dplyr)

#load taxonomy file
data <- read.csv2("taxonomy_tree.csv")

# Create a named list for quick lookup: child -> list(parent, name_en)
node_map <- split(data, data$child)

# Function to build the complete path
build_path <- function(child_id) {
  path <- c()
  current_id <- child_id
  
  while(TRUE) {
    node <- node_map[[as.character(current_id)]]
    if (is.null(node)) break
    path <- c(node$name_en, path)
    parent_id <- node$parent
    if (is.na(parent_id)) break
    current_id <- as.integer(parent_id)
  }
  
  paste(path, collapse = "/")
}

# Apply the function to each row
data <- data %>%
  rowwise() %>%
  mutate(pathString = build_path(child)) %>%
  ungroup()

tree <- as.Node(data, pathName = "pathString", pathDelimiter = "/")

# Function to recursively convert the tree to nested <ul> and <li>
tree_to_html <- function(node) {
  if (node$isLeaf) {
    tags$li(node$name)
  } else {
    tags$li(
      node$name,
      tags$ol(lapply(node$children, tree_to_html))
    )
  }
}

# Convert the entire tree to HTML
html_list <- tags$ul(tree_to_html(tree))

# Print the HTML in your R console
# browsable(html_list)
```

```{r, echo=FALSE, eval=TRUE, results = "asis"}
pathString <- gsub("Statistics Taxonomy/", "", data$pathString)

pathString <- paste0('<li><a href="https://www.sharestats.nl/items-df.html?query=', pathString,'">', pathString, '</a></li>')

cat("<lo>")
cat(pathString[-1], sep='\n')
cat("</ol>")
```
<br>

## Taxonomy for item creation

To add a taxonomy path to your r-exams markdown file, add `exsection:` to the `Meta-information` of your markdown file.

You can copy the desired paths from the list below. You may add multiple path by separating them with a comma. **No new lines allowed though**.

```{}
Meta-information
================
exsection: Descriptive statistics/Summary Statistics/Measures of Location/Median, Descriptive statistics/Summary Statistics/Measures of Spread/Standard Deviation
```
