---
author: Sharon Klinkenberg
page-layout: article
date: now
# image: 
title: Canvas instructions
description: Instructional video on how to upload a sharestats question to Canvas
---

## Upload to Canvas

Canvas packages are already available as download from the ShareStats search table. Follow the instructions below on how to upload the zip file to Canvas.

<!-- Video here -->

## Create Canvas package

It is also possible to download the **ZIP Folder** with all the raw files from the [itembank search page](https://www.sharestats.nl/items-df.html). When you unpack the zip you will have a folder containing the item `.Rmd` file, and data or image files.

We recommend to create a folder your items set this to your working directory and save the extracted ZIP folders in there. In this folder you can ad an R file with the code below to compile the items for uploading.

For compiling the items to a Canvas ZIP you can use the `exams2canvas` funcion from the exams package. Make sure to first install the exams package to R if you do not have it installed already.

```{r, eval=FALSE}
install.packages("exams")
```

You can use the script below to compile a question. Note that you can also download multiple questions and combine them to upload multiple questions at once to canvas.

::: {.panel-tabset}
## Single Question

```{r, eval=FALSE}
library("exams")

# Add file path to list. Multiple paths can be added here list("path1.rmd", "path2.rmd")
file.paths <- list("itemFolder1/itemFile1.rmd")

# Create preview
exams2html(file.paths)

# Set directory where you want to store the .zip package that will be created
directory <- getwd()

# Create TvO package
exams2canvas(file.paths, 
                 dir  = directory, 
                 name = "exam_name")
```

## Multiple Questions

```{r, eval=FALSE}
library("exams")

# Add file path to list. Multiple paths can be added here list("path1/file1.rmd", "path2/file2.rmd")
file.paths <- list("itemFolder1/itemFile1.rmd",
                   "itemFolder2/itemFile2.rmd",
                   "itemFolder3/itemFile3.rmd")

# Create preview
exams2html(file.paths)

# Set directory where you want to store the .zip package that will be created
directory <- getwd()

# Create TvO package
exams2canvas(file.paths, 
                 dir  = directory, 
                 name = "exam_name")
```

:::

The newly created `.zip` file can be uploaded to Canvas as described in the video above.