---
author: Sharon Klinkenberg
page-layout: article
date: now
# image: 
title: TestVision
description: Instructional video on how to upload a sharestats question to TestVision
---

## Download TestVision zip

Testvision packages are already available as download from the ShareStats search table. Follow the instructions below on how to upload the zip file to Testvision.

<iframe width="560" height="315" src="https://www.youtube.com/embed/ogFJaVt3fE8?si=DqGGD3SUfVYH2awp&amp;start=73" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" referrerpolicy="strict-origin-when-cross-origin" allowfullscreen></iframe>

## Manual compile

It is also possible to download the **ZIP Folder** with all the raw files from the search table. When you unpack the zip you will have a folder containing the item `.Rmd` file, and date or image files.

You can compile this to a Testvision package using the `exams2testvision` funcion from the exams package. Make sure to first install the exams package to R if you do not have it installed already.

```{r, eval=FALSE}
install.packages("exams")
```

You can use the following script to compile this question. Note that you can also download multiple questions and combine them in the script below to upload multiple questions at once to TestVision.

```{r, eval=FALSE}
library("exams")

# Add file path to list. Multiple paths can be added here list("path1.rmd", "path2.rmd")
file.paths = list("filepath.rmd")

# Create preview
exams2html(file.paths)

# Set directory where you want to store the .zip package that will be created
directory = ""

# Create TvO package
exams2testvision(file.paths, 
                 dir  = directory, 
                 name = "exam_name",
                 # Make sure no numbers are added to mc questions
                 schoice=list(enumerate = FALSE))
```

The newly created `.zip` file can be uploaded to Testvision as described in the video above.